NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE, PG and PS lipids

### 2017-05-18 Manuscript/manuscript.tex
Add link to the issue
Add results analyzed from from DPPE data delivered by Fernando Favela at https://nmrlipids.blogspot.com/2017/03/nmrlipids-iv-headgroup-glycerol.html?showComment=1492449148750#c3107105122336970292

Comparison between experiments and simulations with CHARMM GUI
parameters for PS lipids in Fig. \ref{HGorderParametersPOPS} suggest that
the model overestimates magnitudes in $\beta$ and g$_3$ order parameters
and forking in $\alpha$.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPS.eps}
  \caption{\label{HGorderParametersPOPS}
    Order parameters for POPS (top) and DOPS (bottom) headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    (DOPS from \cite{browning80} contains 0.1M of NaCl, POPC:POPS mixture from \cite{roux90}).
    Absolute values are shown for experimental data, because signs are not known.
    Simulations values are -S$_{CH}$
  }
  \todo{More simulation data for lipids with different headgroups to be collected} \\
  \todo{Some simulations contain potassium as counterions, while some sodium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.} \\
  \todo{Experimental signs of the order parameters would highly useful.} \\
  \todo{Why there is difference between CHARMM36 simulation results from POPS:POPC mixture and
  pure POPS?}
\end{figure}

>>>>

Absolute values of order parameters between Slipids simulations \cite{??}
and experiments for DPPE are shown in Fig. \ref{HGorderParametersPE}.
Glycerol bakcbone order parameters in Slipids are off from experiments,
as systematically observed in this and previous studies \cite{??}.
Alpha order parameter is too low, but beta shows apparent agreement
with experiments. However, the sign of beta order parameter is positive,
in contrast to PC where negative sign was measured. Thus, the the beta order
parameter agrees with experiment with the assumption that its sign is opposite
than for PC.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPE.eps}
  \caption{\label{HGorderParametersPE}
    Order parameters for DPPE headgroup and glycerol
    backbone from simulations with Slipids \cite{??} and experiments
    (DPPE from \cite{seelig76} and E.coliPE from \cite{gally81}).
    Absolute values are shown, because signs are not known experimentally.
  }
  \todo{Experimental signs of the order parameters would be highly useful.} \\
\end{figure}

Comparison between experiments and simulations with CHARMM GUI
parameters for PS lipids in Fig. \ref{HGorderParametersPOPS} suggest that
the model overestimates magnitudes in $\beta$ and g$_3$ order parameters
and forking in $\alpha$.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPS.eps}
  \caption{\label{HGorderParametersPOPS}
    Order parameters for POPS (top) and DOPS (bottom) headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    (DOPS from \cite{browning80} contains 0.1M of NaCl, POPC:POPS mixture from \cite{roux90}).
    Absolute values are shown for experimental data, because signs are not known.
    Simulations values are -S$_{CH}$
  }
  \todo{More simulation data for lipids with different headgroups to be collected} \\
  \todo{Some simulations contain potassium as counterions, while some sodium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.} \\
  \todo{Experimental signs of the order parameters would highly useful.} \\
  \todo{Why there is difference between CHARMM36 simulation results from POPS:POPC mixture and
  pure POPS? Discussion in https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/1}
\end{figure}
